Output Summary

### 2020-11-21 03-post-process/output-plots.Rmd
Output plots: add time series plots for ocean survival, sex apportionment, and maturity

>>>>

# Ocean Survival

```{r ocean-surv-plots, fig.width = 4, fig.height = 6}
par(mfrow = c(3,2), oma = c(1,1,0,0))
plot_tseries(post_summ(post, "phi_M_O1[.+,1]$"), main = "BON -> O1 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_M_O1[.+,2]$"), main = "BON -> O1 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O1_O2[.+,1]$"), main = "O1 -> O2 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O1_O2[.+,2]$"), main = "O1 -> O2 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O2_O3[.+,1]$"), main = "O2 -> O3 (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O2_O3[.+,2]$"), main = "O2 -> O3 (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
mtext(side = 1, outer = T, line = -0.5, "Brood Year")
mtext(side = 2, outer = T, line = 0, "Survival")
```

# Sex Apportionment

```{r sex-plots, fig.width = 7, fig.height = 4}
par(mfrow = c(1,2), oma = c(1,1,0,0))
plot_tseries(post_summ(post, "^omega[.+,1,1]$"), main = "Natural Origin", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "^omega[.+,1,2]$"), main = "Hatchery Origin", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
mtext(side = 1, outer = T, line = -0.5, "Brood Year")
mtext(side = 2, outer = T, line = 0, "Female Proportion of Esutary Smolts")
```

# Maturity

```{r maturity-plots, fig.width = 4, fig.height = 7}
par(mfrow = c(4,2), oma = c(1,1,0,0))
plot_tseries(post_summ(post, "^psi_O1_Rb[.+,1,1]$"), main = "Age 3 Females (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "^psi_O1_Rb[.+,1,2]$"), main = "Age 3 Females (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "^psi_O1_Rb[.+,2,1]$"), main = "Age 3 Males (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "^psi_O1_Rb[.+,2,2]$"), main = "Age 3 Males (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "^psi_O2_Rb[.+,1,1]$"), main = "Age 4 Females (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "^psi_O2_Rb[.+,1,2]$"), main = "Age 4 Females (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "^psi_O2_Rb[.+,2,1]$"), main = "Age 4 Males (Nat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "^psi_O2_Rb[.+,2,2]$"), main = "Age 4 Males (Hat)", yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))

mtext(side = 1, outer = T, line = -0.5, "Brood Year")
mtext(side = 2, outer = T, line = 0, "Pr(Mature-at-Age|Alive in Ocean)")
